Community Detection for the\\ Generalized Random Dot Product Graph

### 2021-06-14 proposal/prospectus.Rmd
updated prospectus

The SBM, DCBM, and PABM are all special cases of this generative model. Based on the structure of the $\gamma_k$ functions that correspond to each of the SBM, DCBM, and PABM, there are natural choices for clustering algorithms on the embeddings of each of these Block Models, followed by straightforward parameter estimation techniques. Extensions of these results may consider which clustering algorithms result in consistent estimators given restrictions on each of the $\gamma_k$, and how to approach community detection when $\gamma_k$ are unknown altogether.

>>>>

The goal of statistical inference on data sampled from this model would be to estimate each $Z_i$ (community detection) and properties derived from each $\gamma_{Z_i}(T_i)$ (parameter estimation). The SBM, DCBM, and PABM are all special cases of this generative model. Based on the structure of the $\gamma_k$ functions that correspond to each of the SBM, DCBM, and PABM, there are natural choices for clustering algorithms on the embeddings of each of these Block Models, followed by straightforward parameter estimation techniques. For example, in the case of the SBM, we can use GMM on the ASE to estimate community labels, then use the sample means of each community to estimate the edge probabilities. Extensions of these results may consider which clustering algorithms result in consistent estimators for various types of $\gamma_k$, and how to approach this problem when $\gamma_k$ are unknown altogether.

### 2021-06-14 proposal/prospectus.tex
updated prospectus

The SBM, DCBM, and PABM are all special cases of this generative model.
Based on the structure of the \(\gamma_k\) functions that correspond to
each of the SBM, DCBM, and PABM, there are natural choices for
clustering algorithms on the embeddings of each of these Block Models,
followed by straightforward parameter estimation techniques. Extensions
of these results may consider which clustering algorithms result in
consistent estimators given restrictions on each of the \(\gamma_k\),
and how to approach community detection when \(\gamma_k\) are unknown
altogether.

>>>>

The goal of statistical inference on data sampled from this model would
be to estimate each \(Z_i\) (community detection) and properties derived
from each \(\gamma_{Z_i}(T_i)\) (parameter estimation). The SBM, DCBM,
and PABM are all special cases of this generative model. Based on the
structure of the \(\gamma_k\) functions that correspond to each of the
SBM, DCBM, and PABM, there are natural choices for clustering algorithms
on the embeddings of each of these Block Models, followed by
straightforward parameter estimation techniques. For example, in the
case of the SBM, we can use GMM on the ASE to estimate community labels,
then use the sample means of each community to estimate the edge
probabilities. Extensions of these results may consider which clustering
algorithms result in consistent estimators for various types of
\(\gamma_k\), and how to approach this problem when \(\gamma_k\) are
unknown altogether.
